---
title: "R Notebook"
output: html_notebook
---

4.4.1

A financier was interested in estimating the average number of trading days between the announcement of a merger and the effective date of merger. 38 consummated mergers from 1982 in the USA were
randomly selected. The variable measured was:

mergerdays: the number of days between announcement and the effective date of the merger.

The dataset used for this analysis can be found in the s20x package.


```{r}
library(s20x)
data(mergers.df)
head(mergers.df, 3)
```

```{r}
layout20x(1, 2)
hist(mergers.df$mergerdays)
boxplot(mergers.df$mergerdays, main = "Boxplot of merger days")
```

a) Comment briefly on the exploratory analysis of this dataset.

Ans: The median number of days stayed appears to be 89. The spread appears to be around 240 and the data appears to be right skewed.



```{r}
layout20x(1, 1)
summaryStats(mergers.df$mergerdays)
```
```{r}
normcheck(mergers.df$mergerdays)
```



b) What can we conclude from the output of normcheck(mergers.df$mergerdays)?

Ans: The data points don't lie on a line on the QQ plot. So, the normality of the data is not valid.


c) Suppose we did find a confidence interval for the mean number of days between the announcement
and actual merger. Would that analysis be valid?

Ans: Yes, as the Central Limit THeorem would apply as we have n=36 observations.

```{r}
normcheck(log(mergers.df$mergerdays))
```

d) Has a log transformation improved the situation with regards to modelling assumptions?

Ans: Yes, now the normality of the data seems to be valid as seen from the data points on the line on the QQ plot.

```{r}
t.test(log(mergers.df$mergerdays))
```
```{r}
exp(t.test(log(mergers.df$mergerdays))$conf.int)
```

e) What can we conclude from the p-value of the t-test?

Ans: We have strong evidence against the null hypothesis that the median number of days between announcement and the effective date is 0. However, this is not useful to us.

f) Write a brief Executive Summary detailing the findings from this analysis.

Ans: We are interested in finding the number of days between the announcement of a merger and the effective date of the merger for companies from 1982, USA based on 38 mergers.

We had to transform these data in order to perform the analysis. As a consequence, our analysis estimates the median number of days between the two events.

We estimate that the number of days between the two events to be between 79 days and 107 days for mergers in US in 1982.