---
title: "R Notebook"
output: html_notebook
---

**4.4.3 **

Failures in aircraft gas turbine engines due to high cycle fatigue is a pervasive problem. A single crystal nickel base superalloy was designed and manufactured to address this problem. We are interested in fitting a model to estimate mean cycles to failure from strain amplitude for turbine blades made of this new material.

The variables recorded are:
*Strampl* strain amplitude
*Cycfail* cycles to failure

From previous analyses, we suspect that a multiplicative relationship exists between the two variables.


```{r}
library(s20x)
gasturbines.df = read.table("gasturbines.txt", header = TRUE)
head(gasturbines.df)
```
```{r}
plot(Cycfail~Strampl, data = gasturbines.df)
```


```{r}
eovcheck(Cycfail~Strampl, data = gasturbines.df)
```

a) Explain briefly whether the first residual plot (eovcheck(gasturbines.lm)) confirms our suspicion that there might be a multiplicative relationship?

Ans: Yes because we see the fan effect in the residual plot.


```{r}
gasturbines2.lm = lm(log(Cycfail)~Strampl, data = gasturbines.df)
cooks20x(gasturbines2.lm)
```

b) Does modcheck(gasturbines2.lm) show any issues with the model fitted?

Ans: Data point 6 has a Cook's distance of more than 0.4. This data point appears to be significant.

```{r}
summary(gasturbines2.lm)
```


```{r}
gasturbines3.lm = lm(log(Cycfail)~Strampl, data = gasturbines.df[-6, ])
summary(gasturbines3.lm)
```


```{r}
cooks20x(gasturbines3.lm)
```





```{r}
cooks.distance(gasturbines3.lm)
```
```{r}
summary(gasturbines3.lm)
```
d) Write down the equation of the final model fitted

Ans: log(Cycfaili) = meanStrampl + ei where ei ~ iid N(0, sd^2).

e) Which of the two back-transformed confidence intervals for the regression coefficient of Strampl
should we interpret? Explain your answer briefly.

Ans: Interval 2 because interval 1 is too wide.

```{r}
100 * (exp(confint(gasturbines2.lm)) - 1)
```


f) Write a brief Executive Summary of the main conclusions you would draw from the analysis.

Ans: 


g) Give a prediction for a single gas turbine’s cycles to failure for a strain amplitude of 0.01. Can
we trust this prediction?

Reference:
Arakere N. K., Swanson G. G. (2000) Effect of Crystal Orientation on Fatigue Failure of Single Crystal
Nickel Base Turbine Blade Superalloys. ASME. J. Eng. Gas Turbines Power. 124(1):161-176.
Devore, J. L. (2016). Probability and Statistics for Engineering and the Sciences, 9e. Boston, MA:
Cengage Learning.

