---
title: "Case Study 4"
output: html_notebook
---


```{r}
library(s20x)
data(house.df)
head(house.df)
```

```{r}
priceDiff = house.df$advertised.price - house.df$sell.price
boxplot(priceDiff)
```
```{r}
summaryStats(priceDiff)
```

```{r}
normcheck(priceDiff)
```

```{r}
t.test(priceDiff)
```
**Methods and Assumptions**

The data is paired, so we use a paired t-test.

The data is assumed to be independent. The points on the Q-Q plot seems to be right-skewed slightly. However, we can use Central Limit Theorem to assume that the data follows normality.

The data is modeled as diffPricei = mu + ei where diffPricei is the difference in the advertised and the actual house price, mu is the mean difference and ei ~iidN(0, sd^2).


**Executive Summary**

We were interested in finding out if there was a difference in the advertised price and the selling price for houses in Mt Eden. The data contained 100 random houses.

Since our original data involved two measurement on each house (the advertised price and the selling price), the difference between the two prices for each house has been analysed.

On average, the advertising price was found to be between 22140 NZD and 26475 NZD more than the selling price.

We concluded that there is a significant difference between the mean sale price and the mean advertised price for houses sold in Mt Eden.
